---
output:
  pdf_document: default
  html_document: default
---


# Badges in Stack Overflow

```{r label = "global-options", echo=FALSE, message=FALSE, highlight=TRUE}
knitr::opts_chunk$set(
        message = F,
        error = F,
        warning = F,
        comment = NA,
        highlight = T,
        prompt = T
        )

### some initialization for Stack Overflow

# My personal user number on Stack Overflow: 
petzi <- 7322615 # for test purposes

# Available actions (I added "timeline"):
so_actions <- c("answers", "badges", "comments", "favorites", "mentioned", "network-activity", "posts", "questions", "reputation", "reputation-history", "suggested-edits", "tags", "top-answer-tags", "top-question-tags", "top-tags", "privileges", "notifications", "moderators", "timeline")


```

## The Stack Exchange Network

### 172 Websites with Stack Overflow as Showpiece

Why I am using Stack Overflow as my primary example to investigate the usefulness of badges in education? 

[Stack Overflow](https://stackoverflow.com/) is a very successful Question and Answer (Q&A) website. It hosts the world’s largest programming community and is still growing. Stack Overflow occupies about the 60th position in the world rankings of websites. Currently (June 2018) it has 8.9 million registered user with 16 million questions and 25 million answers. There are already clones in different languages (Russian , Japanese, Spanish and Portuguese) whose user basis at least are partially to add.

But Stack Overflow is just the [flagship of StackExchange](https://stackexchange.com/sites#traffic), a network of (currently) 173 Q&A websites, following the same principles for community management. With this high number of Q&A websites for different issues and target groups it is allowed to assume that at least some principles of the successful community management of programmer are not only restricted to technical subjects but can be transferred to other areas as well. One can see from the [graphical represenation](https://stackexchange.com/sites?view=grid#) of the Stack Exchange sites that technology, "hard sciences" like mathematics, physics, chemistry dominate the network. But there are also websites on philosophy, language learning and even websites addressing recreational issues like bicycles, chess and beer, wine & spirits. 

> Stack Exchange network consists of 173 Q&A communities including Stack Overflow, the largest, most trusted online community for developers to learn, share their knowledge, and build their careers. (Quote from the Stack Overflow website) ^[This quote apears in a little window when you are on the [meta site](https://meta.stackexchange.com) and you click in the StackExchange banner left from the search field. But actually in my downloaded data I found just 172 websites. On the about site of [StackExchange](https://stackexchange.com/about) however I have seen outdated information from the year 2015 (Today: 25th May 2018). You can find another summary of the astonishing success story of StackOverflow from a business perspective on the [company page of StackOverflow](https://stackoverflow.com/company). -- It is sometimes difficult for me to find the right place for some information because of the complex clutter of (similar) sites on different levels (site and meta site).]

### "Graduates" Websites and Websites on Trial (Beta)


```{r group-by-site-state, echo=FALSE, eval=FALSE}
my_packages <- c("tidyverse", "knitr", "kableExtra", "anytime")
temp <- lapply(my_packages, library, character.only = TRUE)

sites <- readRDS("data-processed/sites.rds")
sites <- rowid_to_column(sites, var = "#")

sites_state <- info_tbl[-c(2, 4:26, 28:34)]
sites_state <- sites_state[, c(2,1)]

sites_state <- sites_state %>% as_tibble() %>% mutate(
    site_state = if_else(
        is.na(info_tbl$site_launch_date), # check if NA
        info_tbl$site_state <- "Beta", # mark as beta
        info_tbl$site_state <- "Normal"
    )
)

by_state <- sites_state %>% group_by(site_state)
sites <- by_state %>% summarise(
    users = sum(total_users),
    n = n()
)

knitr::kable(sites, 
        booktabs = T, 
        longtable = F,
        row.names = F,
        col.names = c("Status", "Users", "Sites"),
        caption = "StockExchange Websites by their Status") %>%
        column_spec(1, width = "2cm")  %>%
        column_spec(2, width = "3cm")  %>%
        column_spec(3, width = "2cm")
```

### Stack Exchange Websites by Subject




```{r display-site-infos, echo=FALSE}
my_packages <- c("tidyverse", "knitr", "kableExtra", "anytime")
temp <- lapply(my_packages, library, character.only = TRUE)

sites <- readRDS("data-processed/sites.rds")

sites <- sites[order(sites$total_users, decreasing = TRUE), ] # sort by number of users
sites <- rowid_to_column(sites, var = "site_rank") # set  1…n to column variable
sites <- sites[order(sites$site_name), ]   # sort by name and remember rank by user

# sites <- sites[, c("site_site_state",
#                  "total_users",
#                  "site_api_site_parameter"
#                  )]

sites2 <- sites %>% select(
    site_rank,
    site_name,
    total_votes
)

# sites2 <- sites[, c(
#     site_rank, 
#     total_users,
#     total_votes)]



# names(sites[2]) <- paste0(names(sites[2]),
#                           footnote_marker_alphabet(1, "latex"))
# names(sites[7]) <- paste0(names(sites[7]),
#                           footnote_marker_alphabet(2, "latex"))

# sites1 <- as_tibble(data.frame(
#     sites$site_rank,
#     Value   = sites$total_users,
#     Third_3 = sites$total_votes
# ))



sites2 %>% 
    kable(
      # booktabs = T,
      # longtable = T,
      # row.names = T,
      # caption = "StockExchange Network (May 25th, 2018)",
      escape = F,
      col.names = linebreak(c("Status", "Users", "Rank\n(Users)")))


# knitr::kable(sites,
#         booktabs = T,
#         longtable = T,
#         row.names = F,
        # escape = F,
        # col.names = c("Nr.",
        #               "Rank",
        #               "Name",
        #               "Users",
        #               "Audience",
        #               "URL"),
        # caption = "StockExchange Network (May 25th, 2018)") %>%
        # kable_styling(latex_options =
        #         c("striped", "repeat_header", full_width = T)) %>%
        # column_spec(1, width = "2.5cm")  %>%
        # column_spec(2, width = "3.5cm")  %>%
        # footnote(alphabet = c(
        #     "rank acoording to number of users",
        #     "B = launch date of open beta, N = launch of normal status")
        # )


```


## Dynamics of the Stack Exchange Community

But before to look into these other websites one should grasp the community dynamics of the most successful member of the network. 

All Stack Exchange websites are based of a complex interplay between different elements:

1. **Scores ("reputation" points)** are earned through positive votes by peers for posting useful answers but also for asking questions, if they show research effort and their underlying problems are reproducible.
2. **Badges** as digital token in form of emblems. They are awarded by the system either for fulfilling certain tasks or reaching a certain amount of community awareness. 
3. **Priviliges** are granted when certain thresholds or milestones of reputation points are transcended. Each privilege opens up a specified user rights in relation to the website. 

I am convinced that the study of user interactions of Stack Overflow can be very helpful to understand the success factors for a prosperous community building process. To study user behavior and their reactions to the rules and framework of Stack Overflow one can learn not only much about the effects of gamification elements (e.g. the interplay between reputation points and badges) but also how communities of practice work.

Besides the common review of literature my research in this paper is based on four sources:

1. **[Stack Overflow](https://stackoverflow.com/):** Clearly enough this has to be one of my chief source of information.
2. **[Stack Exchance API](http://api.stackexchange.com/):** The Stack Exchange network provides an Application Programming Interface (API) where one can download data for answering research question. 
3. **[Meta Stack Overflow](https://meta.stackoverflow.com/):** This website is especially dedicated to Q&A _about_ Stack Overflow itself. The discussion on this website is an important resource on qualitative data to my research question.
4. **[Meta Stack Exchange](https://meta.stackexchange.com/):** Another for meta-discussion. This time for the whole Stack Exchange family of Q&A websites, so to speak the meta-meta-website of the Stack Overflow website.

## Categorization of Badges

I need to download all types of badges with their description and for further investigation to categorize them. 


### Badges for different activities

The badges are grouped according to the necessary activities to get them. The long version what you have to do to get a a specific badge is posted on meta.stackexchance.com under the title: [List of all badges with full descriptions](https://meta.stackexchange.com/questions/67397/list-of-all-badges-with-full-descriptions). A short and more readable version can be seen on  [help page for badges](https://stackoverflow.com/help/badges):

1) Question badges
2) Answer badges
3) Participation badges
4) Moderation badges
5) Other badges
6) Documentation badges

### Badges from different sources 

Another differentiation is the point of origin the badges come from. Even though all badges are generated automatically by the system, there are two principal sources to get them. There are two different entities responsible for awarding badges. 

* There are badges you can get by just doing a certain action once or a needed number of times. * And there are badges you get only after some community action. 

I call the first type `user` and the second type `peer` badges.

**Examples for `user` badges:**

* Name: "Civic Duty" (Vote 300 times). 
* Name: "Enthusiast" (Visit the site each day for 30 consecutive day)

Some of the `user` badges are only available after some threshold value is reached and a certain privileges is granted. For instance voting up needs 15 and voting down 125 reputation points. 

**Examples for `peer` badges:**

* Name: "Favorite Question" (Question favored by 25 users)
* Name: "Popular Question" (Question with 1000 views).

There are also badges tied with certain events, like moderator election, working with the beta version, meeting employees at an event etc. Mostly these badges are in my categorization `user` badges, but you cannot get them at any time, even if you would have the required privileges.

The badge system of Stack Overflow is a dynamic system. When the website was launched (September 15, 2008) it did not start with all 91 badges which are listed today (May 21, 2018). Some of the badges were added during the history of the website but other are not awarded anymore. Some of those badges which are not functional anymore are retired badges (e.g. "Analytical", for visiting all sections of the FAQ). This means you will still see some veteran users with these badges. Other badges (all three documentation badges for instance) are withdrawn, e.g. they were even deleted from those user accounts they were awarded earlier. I call these two groups of badges `event` and `dead` badges.

To sum up there are 4 points of origin for badges:

1) Badges from user action = `user` badges
2) Badges from community action = `peer` badges
3) Badges from some action during a specified occurrence = `event` badges
4) Badges where the point of origin is not interesting anymore as they are now non-functional = `dead` badges  

### Badges with different degrees of difficulty

Badges are ranked by their difficulty. According to their level of difficulty users are awarded with bronze (relatively easy), silver (moderately difficult) or gold (difficult) badges. 

There are badges with the same action required but with different amount of repetition. User can see those groups of badges separated by lines on the [Stack Overflow website](https://stackoverflow.com/help/badges). On this page one can also inspect how many time each badge was awarded.

There is also a special group of badges intimately linked with reputation of the user's expertise. These `Tag Badges` also come with different degrees of difficulty.

I will focus in my research on those badges where users are mainly responsible. Those are the badges where I can show if users are motivated to strive for them. 



**Visit the site each day for […] consecutive days. (Days are counted in UTC.)**

* 30 (Enthusiast)
* 100 (Fanatic)

**Ask a well-received question […] and maintain a positive question record**

* on 5 separate days (Curious)
* on 30 separate days (Inquisitativ)
* on 100 separate days (Socratic)

**Complete at least […]. This badge is awarded once per review type**

* one review task (Custodian)
* 250 review tasks (Reviewer)
* 1000 review tasks (Steward)

**Edit and answer […] (both actions within 12 hours, answer score > 0)**

* 1 question (Explainer)
* 50 questions (Refiner)
* 500 questions (Illuminator)

**Edit**

* first post (Editor)
* 80 posts (Strunk & White)
* 500 posts (Copy Editor)

**Edit […] that was inactive for 6 months**

* first post (Excavator)
* 100 posts (Archaeologist)


The `user` badges are of utmost importance for my research. Most of these badges are granted for quality assurance work on the website and are not linked with reputation points. They are -- from a systemic perspective -- important for the dynamic of the website and maintain respective raise the quality of the platform and their ecological sustainability.

When I can show that people are striving to get `user` badges -- even when they are not linked with reputation points -- than it is evident that badges are some additional (motivational) factors for the community development.





```{r display-badges-table-landscape, echo=FALSE}
my_packages <- c("dplyr", "knitr", "kableExtra")
temp <- lapply(my_packages, library, character.only = TRUE, warn.conflicts = FALSE)

badges_table <- readRDS("data-processed/badges.rds")
        
kable(badges_table, 
        booktabs = T, 
        longtable = T,
        row.names = T,
        col.names = c("ID", "Name", "Count", "Rank",
                           "Activity", "Origin", "Alike", "Description"),
        caption = "Badges in Stack Overflow") %>%
        kable_styling(latex_options = 
                c("striped", "repeat_header", full_width = T)) %>%
        column_spec(3, width = "2cm") %>%
        column_spec(9, width = "9cm") %>%
        landscape()
```



