# Test miscellanous things


```{r label = "global-options", echo=FALSE, highlight=TRUE}
knitr::opts_chunk$set(
        message = F,
        error = F,
        warning = F,
        comment = NA,
        highlight = T,
        prompt = T
        )

### install and load some important packages
### https://github.com/tidyverse/tidyverse
if (!require("tidyverse"))
        {install.packages("tidyverse", repos = 'http://cran.wu.ac.at/')
        library(tidyverse)}

### above command installed and loaded the core tidyverse packages:
# ggplot2: data visualisation
# tibble:  a modern take on data frames
# tidyr:   data tidying
# readr:   data import (csv, tsv, fwf)
# purrr:   functional R programming
# dplyr:   data (frame) manipulation
# stringr: string manipulation
# forcats: working with categorial varialbes

### My personal reminder for other important packages:
### Working with times:
# hms, for times.
# lubridate, for date/times.

### Importing other types of data:
# feather, for sharing with Python and other languages.
# haven, for SPSS, SAS and Stata files.
# httr, for web apis.
# jsonlite for JSON.
# readxl, for .xls and .xlsx files.
# rvest, for web scraping.
# xml2, for XML.

### Modelling
# modelr, for modelling within a pipeline
# broom, for turning models into tidy data

if (!require("lubridate"))
        {install.packages("lubridate", repos = 'http://cran.wu.ac.at/')
        library(lubridate)}
if (!require("stackr"))
        {install.packages("stackr", repos = 'http://cran.wu.ac.at/')
        library(stackr)}
if (!require("jsonlite"))
        {install.packages("jsonlite", repos = 'http://cran.wu.ac.at/')
        library(jsonlite)}
if (!require("dlstats"))
        {install.packages("dlstats", repos = 'http://cran.wu.ac.at/')
        library(dlstats)}

# source("stackr-api-utilities.R")
```

## Install stackr with vignettes

Building vignettes takes some time. So if you are in a hurry, than just install stackr. You can still look at the vignettes in R help. The difference is: With `build_vignettes = TRUE` and then `browseVignettes("stackr")` you can look at the vignettes in your default browser. This is slightly more comfortable.

```{r install-stackr, eval=FALSE}
devtools::install_github("dgrtwo/stackr", build_vignettes = TRUE)
browseVignettes("stackr")
```

## Load several packages at once

The following code is part of a debate at SO with different suggestions. It seems to me, that all suggestions (utility packages, code examples) has some disadvantages:

* **lapply:** For me the [best](https://stackoverflow.com/questions/8175912/load-multiple-packages-at-once) approach -- it uses just `lapply`. I have changed `require` to `library` because of the arguments by [Yihui](https://yihui.name/en/2014/07/library-vs-require/). My lines now gives a error message and stops if one of the called packages is not installed.
* **easypackages:** is not available on CRAN anymore, has very poor downloads.
* **pacman:** a very sophisticated programm, but -- for me at least -- to complex and therefore to much overhead.
* **installed.packages:** [ipak.R](https://gist.github.com/stevenworthington/3178163) This loads _and_ installs missing packages. It is quite similar as `lappy`-version, but -- because of the if-condition -- more complex. Additionally it is checking which packages are installed: 

> "This can be slow when thousands of packages are installed, so do not use this to find out if a named package is installed (use system.file or find.package) nor to find out if a package is usable (call require and check the return value) …"

So maybe the best would be to combine the `lapply` with the `installled.packages`
 version. But insted to use `installled.packages` I should use in the if-statement `require`, check for the return value and -- if necessary -- to install missing packages.
 
```{r load-several-packages-at-once, eval=FALSE}
x <- c("plyr", "psych", "tm")
lapply(x, library, character.only = TRUE)
```


## How many downloads of a defined packages?


```{r download-stats}
library(dlstats)
y <- cran_stats("learnr")
ggplot(y, aes(start, downloads, group = package, color = package)) +
        geom_line() + geom_point(aes(shape = package))
# cranApp()
```

## Some data to remind

1. How to find answers tagged with `r` and not active since 6 month: [Search](https://stackoverflow.com/search?q=%5Br%5D+lastactive%3A..6m+is%3Aa)

<!-- 2. My personal user number: `r petzi <- 7322615` -->

3. What kind of actions are are allowed with `combine_url`?

I have added `timeline` to the list!

`r actions <- c("answers", "badges", "comments", "favorites", "mentioned", "network-activity", "posts", "questions", "reputation", "reputation-history", "suggested-edits", "tags", "top-answer-tags", "top-question-tags", "top-tags", "privileges", "notifications", "moderators", "timeline")`


## Some experiments

```{r some-experiments, echo=FALSE, eval=FALSE}

# knitr::kable(badges, caption = "Type of Badges in Stack Overflow")
# knitr::kable(by_activity, caption = "Main Types of Badges in Stack Overflow")
# knitr::kable(by_origin, caption = "User and Community Badges in Stack Overflow")


# # user_info <- stack_users(id = user_petzi,
# #                          special = "badges",
# #                          pagesize = 100,
# #                          page = 1,
# #                          num_pages = 1000
# # )
# # user_timeline <- stack_users(id = 7322615,
# #                          special = "reputation-history”",
# #                          pagesize = 100,
# #                          page = 1,
# #                          num_pages = 1000
# # )
# 
# # user_timeline1 <- combine_url(base = "users",
# #         id = 7322615,
# #         special = "timeline")

# x1 <- stack_GET("users/id", id = 7322615)
# 
# x2 <- stack_GET("http://api.stackexchange.com/docs/timeline-on-users#ids=7322615&filter=default&site=stackoverflow&run=true"
#                 )

# privileges <- stack_privileges()
```

```{r try-out, echo=FALSE, eval=FALSE}

url <- stackr:::combine_url(base = "users", 
                            id = c(9371451),
                            special = "timeline",
                            special_ids = actions)
df_user <- stackr:::stack_GET(url, num_pages = 15)


```

```{r get-badges-for-views-on-consecutive-days, echo=FALSE, eval=FALSE}
badges_consecutive <- stack_badges(c(71,83), "recipients")

```



```{r get-user-history, echo=FALSE, eval=FALSE}
library("jsonlite")

# I need a loop, 
# whenever json_list[["has_more"]] == TRUE than run annother page
# this new database rbind with the previous one
# maybe there is also a direct method after looking at the programm code of stackr

json_file1 <- "https://api.stackexchange.com/2.2/users/7322615;3566854;1556049;2545523/timeline?page=1&pagesize=100&site=stackoverflow&key=mRTYimh499J3lInIGjcxfA(("
json_list1 <- jsonlite::fromJSON(json_file1, flatten = TRUE)
df1 <- as.tibble(json_list1[[1]])
df1 <- df1 %>% mutate(created = with_tz(as.POSIXct(creation_date, origin = "1970-01-01"), "UTC"))
# df2 <-
#         data.frame(matrix(unlist(json_list2[[2]]), nrow = 10, byrow = T), stringsAsFactors =
#         FALSE)

# json_data <- json_data[[1]] <- NULL
# df <- as.tibble(json_data)

```

